---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  collapse = TRUE,
  comment = "#>"
)
```

# Teaching datasets for Lecture Series on Open Reproducible Science in R

<!-- badges: start -->
[![License for data](https://img.shields.io/badge/license (for data)-CC0-blue.svg)](https://creativecommons.org/publicdomain/zero/1.0/)
<!-- badges: end -->

This repository contains a collection of teaching datasets that can be used for teaching [R](https://cran.r-project.org). Although this repository was created specifically for use in teaching the [Open Reproducible Science in R](https://oxford-ihtm.io/open-reproducible-science) lecture series, the data made available through here is open for access and use by anyone and is distributed under a Creative Commons 1.0 Universal (CC0) license.

## Dataset description

```{r data-description}
file_names <- list.files() |>
  (\(x) x[stringr::str_detect(string = x, pattern = "README|teaching_datasets", negate = TRUE)])()

file_types <- file_names |>
  stringr::str_split(pattern = "\\.", simplify = TRUE) |>
  (\(x) x[ , 2])() |>
  toupper()

file_description <- vector(mode = "character", length = length(file_types))

file_description[file_names == "south_wollo_coverage.csv"] <- "A dataset from a Community-based Management of Acute Malnutrition (CMAM) programme in South Wollo Zone, Ethiopia"


data.frame(file_names, file_types, file_description) |>
  knitr::kable(row.names = FALSE, col.names = c("File Name", "File Type", "File Description"))

```





